2. Simulated Data

### 2021-06-30 analysis/reports/rmd/02_dataProcessing.Rmd

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = FALSE)
library(data.table)
library(magrittr)
library(stringr)
library(glue)
library(DescTools) # gini coefficient
library(kableExtra)
library(downloadthis)
```

@@

This report is the second in a series of reports covering this project. It explains how simulated data is processed and prepared for analyses.

>>>>

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

library(data.table)
library(magrittr)
library(stringr)
library(glue)
library(DescTools) # gini coefficient
library(kableExtra)
library(downloadthis)
```

@@

[This report](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd/02_dataProcessing.Rmd) is the second in a series of reports covering this project. It explains how simulated data is processed and prepared for analyses.
